### 2025-01-16 analysis/preprocessing.qmd
chore(preprocessing): update feature_n
- feature_n encodings now reflect changes to bib/extractions.bib -exclusions updated - grekow2021mu now appears in regression studies

R_studies$feature_n[R_studies$feature_n==" 548; after reduction, 139 for PCA and 276 for ReliefF   "] <- 548

R_studies$feature_n[str_detect(R_studies$feature_n,'pre_fitting')] <- 21
R_studies$feature_n[str_detect(R_studies$feature_n,'but 15 reported')]<-15
R_studies$feature_n[str_detect(R_studies$feature_n,'50 PCA features')]<-50
R_studies$feature_n[str_detect(R_studies$feature_n,'548 dimensions. Pos')]<-548
R_studies$feature_n[str_detect(R_studies$feature_n,'60 handcrafted and')]<-60 # this should be 14400+60!
R_studies$feature_n[str_detect(R_studies$feature_n,'before_selection = 45')]<-45
R_studies$feature_n[str_detect(R_studies$feature_n,'model 4 = 388')]<-388
R_studies$feature_n[str_detect(R_studies$feature_n,'6670 in MediaEval')]<-6670
R_studies$feature_n[str_detect(R_studies$feature_n,'557 before feature')]<-557
R_studies$feature_n[str_detect(R_studies$feature_n,'not specified')]<-NA
R_studies$feature_n<-as.numeric(R_studies$feature_n)

@@

```{r}
#| echo: true
#| eval: true
R_studies$citekey <- factor(R_studies$citekey) # 21 unique values
R_studies$dimension <- factor(R_studies$dimension)

@@

R_studies$feature_n[R_studies$feature_n==" 15; 23 in table, but 15 reported  "] <- 15 #resolved from the paper

R_studies$feature_n[R_studies$feature_n==" 15; 23 in table, but 15 reported  "] <- 15 #resolved
R_studies$feature_n[R_studies$feature_n==" before_selection = 45, after_selection = 6  "] <- 45 #resolved
R_studies$feature_n[R_studies$feature_n==" model 1: 52, model 2 = 68, model 3 = 260, model 4 = 388 "] <- 388 #resolved
R_studies$feature_n[R_studies$feature_n==" variable, 557 before feature selection "] <- 557 #resolved

R_studies$feature_n[R_studies$feature_n==" 50 PCA features "] <- 499 #resolved

R_studies$feature_n[str_detect(R_studies$feature_n,'150 PCA features')] <- 3000
R_studies$feature_n[str_detect(R_studies$feature_n,'pre_fitting = 21')] <- 21
R_studies$feature_n[str_detect(R_studies$feature_n,'548 dimensions')] <- 548
R_studies$feature_n[str_detect(R_studies$feature_n,'548; after reduct')] <- 548
R_studies$feature_n[str_detect(R_studies$feature_n,'60 handcrafted and filter bank')] <- 3600
R_studies$feature_n[str_detect(R_studies$feature_n,'Features deep-learned from audio (not specified) but 1802 in DEAM')] <- 260

# 2024-10-21: I changed the encoding for this one to "150 PCA features", so updated above.
# R_studies$feature_n[str_detect(R_studies$feature_n,'not specified')] <- 3000 # under-estimation based openSmile features and the paper arguing that they have 15 stat moments

R_studies$feature_n<-as.numeric(R_studies$feature_n)

print(quantile(R_studies$feature_n,c(0.333,0.666),na.rm = T))
#quantile(R_studies$feature_n,c(0.25,0.50,0.75),na.rm = T)

@@

#table(C_studies$feature_n)
C_studies$feature_n[str_detect(C_studies$feature_n,'eight different ')]<-600 # arbitrary!
C_studies$feature_n[str_detect(C_studies$feature_n,'126, retained 97')]<-126 
C_studies$feature_n[str_detect(C_studies$feature_n,'1702; best model uses 100 after reduction')]<-1702 #  arbitrary!
C_studies$feature_n[str_detect(C_studies$feature_n,'548; after reduction, ')] <- 548 
C_studies$feature_n[str_detect(C_studies$feature_n,'548 dimensions')] <- 548 
C_studies$feature_n[str_detect(C_studies$feature_n,'548. Post-reduction')] <- 548 
C_studies$feature_n[str_detect(C_studies$feature_n,'8; 3 after')]<-8 
C_studies$feature_n[str_detect(C_studies$feature_n,'between 9 and 10')]<-10 
C_studies$feature_n[str_detect(C_studies$feature_n,'summarize feature')]<-600 # arbitrary
#table(C_studies$feature_n)

>>>>

```{r}
#| echo: false
#| eval: true
# this entry no longer appears due to exclusion:
# R_studies$feature_n[R_studies$feature_n==" 548; after reduction, 139 for PCA and 276 for ReliefF   "] <- 548
# R_studies$feature_n[str_detect(R_studies$feature_n,'548 dimensions. Pos')]<-548
R_studies$feature_n[str_detect(R_studies$feature_n,'pre_fitting')] <- 21
R_studies$feature_n[str_detect(R_studies$feature_n,'but 15 reported')]<-15 #resolved from the paper
R_studies$feature_n[str_detect(R_studies$feature_n,'150 PCA features')]<-3000 #discuss
R_studies$feature_n[str_detect(R_studies$feature_n,' 50 PCA features')]<-  499 #resolved
R_studies$feature_n[str_detect(R_studies$feature_n,'60 handcrafted and')]<-60 # this should be 14400+60! discuss
R_studies$feature_n[str_detect(R_studies$feature_n,'before_selection = 45')]<-45 #resolved
R_studies$feature_n[str_detect(R_studies$feature_n,'model 4 = 388')]<-388 #resolved
R_studies$feature_n[str_detect(R_studies$feature_n,'6670 in MediaEval')]<-6670 #discuss
R_studies$feature_n[str_detect(R_studies$feature_n,'557 before feature')]<-557 #resolved
# this seems to refer to yang2021an, which is handled above with "6670 in mediaeval"
# R_studies$feature_n[str_detect(R_studies$feature_n,'not specified')]<-NA
# 2025-01-15
# beveridge2018po. This one is worth discussing as the two studies might be worth differentiating. 
# Using higher value for now. DISCUSS
R_studies$feature_n[str_detect(R_studies$feature_n,'study 1: 26, study 2: 28')] <- 28
R_studies$feature_n<-as.numeric(R_studies$feature_n)

@@

```{r}
#| echo: true
#| eval: true
R_studies$citekey <- factor(R_studies$citekey) # 22 unique values
R_studies$dimension <- factor(R_studies$dimension)

@@

```{r}
#| echo: false
#| eval: true
print(quantile(R_studies$feature_n,c(0.333,0.666),na.rm = T))
#quantile(R_studies$feature_n,c(0.25,0.50,0.75),na.rm = T)

@@

#table(C_studies$feature_n)
C_studies$feature_n[str_detect(C_studies$feature_n,'eight different ')]<-600 # arbitrary!
C_studies$feature_n[str_detect(C_studies$feature_n,'126, retained 97')]<-126 
C_studies$feature_n[str_detect(C_studies$feature_n,'1702; best model uses 100 after reduction')]<-1702 #  arbitrary!
# these seem to refer to the excluded bai studies
# C_studies$feature_n[str_detect(C_studies$feature_n,'548; after reduction, ')] <- 548 
#C_studies$feature_n[str_detect(C_studies$feature_n,'548 dimensions')] <- 548 
# C_studies$feature_n[str_detect(C_studies$feature_n,'548. Post-reduction')] <- 548 
C_studies$feature_n[str_detect(C_studies$feature_n,'8; 3 after')]<-8 
C_studies$feature_n[str_detect(C_studies$feature_n,'between 9 and 10')]<-10 
C_studies$feature_n[str_detect(C_studies$feature_n,'summarize feature')]<-600 # arbitrary
#table(C_studies$feature_n)
